Using forecasting models for new book publishing

### 2015-07-22 paper.tex
traduciendo

The rest of this paper is structured as follows:
%Section \ref{sec:soa} presents a comprehensive review of the approaches found in the bibliography to BLA BLA BLA.
Section \ref{sec:methodology} briefly describes the EA algorithm, and analyzes the parameters we propose to evaluate.
This section also presents the experimental setup and the methodology considered in the study. 
Section \ref{sec:experiments} details the statistical study based on ANOVA. 
Obtained results are analyzed in order to establish the most suitable values.
Finally, conclusions and future work are presented in Section \ref{sec:conclusionsAndFutureWork}.

@@

@@

\subsection{Data collection and analysis}

@@

\subsection{Selecting an appropriate forecasting method}

@@

\subsection{Applying forecasting methods to solve the problem}

>>>>

The rest of this paper is structured as follows:
%Section \ref{sec:soa} presents a comprehensive review of the approaches found in the bibliography to BLA BLA BLA.
Section \ref{sec:problem} describes the new book publishing problem, followed by Section \ref{sec:methodology} where the experimental setup and the methodology considered in the study is presented. 
Section \ref{sec:experiments} reports and analyzes the obtained results with a real data set.
Finally, conclusions and future work are presented in Section \ref{sec:conclusionsAndFutureWork}.

@@

Describir en detalle el problema de la tirada editorial. 
Comentar que se ha colaborado con la empresa Trevenque, y qué datos nos ha pasado.
Indicar qué variables externas afectarán a las predicciones, etc.

@@

%-------------------------------------------------
\subsection{Data collection and analysis}

@@

%-------------------------------------------------
\subsection{Selecting an appropriate forecasting method}

@@

%-------------------------------------------------
\subsection{Applying forecasting methods to solve the problem}
